---
title: "DC Analysis"
output:
  pdf_document: default
  html_notebook: default
editor_options: 
  markdown: 
    wrap: 72
---
***NOTE! This uses cleaned data. You can run this on its own if you are using the cleaned data file from GitHub. If you are using raw ACS sata, run the "Data Cleaning" file before this.***


## Libraries and Data
```{r Libraries, warning=FALSE}
#load libraries
library(ipumsr)
library(dplyr)
library(rdrobust)
library(ggplot2)
library(rddtools)
library(gridExtra)
```

```{r}
# load cleaned data
#dcmoms <- read.csv("clean_data_dc_moms.csv")
```

## Regression Discontinuity Analysis

Below, I run a regression discontinuity analysis using Washington DC data. I create a model for 2, 3, 4, and 5 years after DC's preschool program was implemented. My running variable is the age of a woman's youngest child. First, I use educational attainment and the rate of mothers with college degrees as my outcome variables.

### Educational Attainment

```{r DC 5 years educ}
#dc rdd 5 years after implementation, educational attainment

#create initial subset
dc5yrs <- subset(dcmoms, dcmoms$YEAR == 2014)

#create data table for regression
dc5yrs_reg <- rdd_data(y = dc5yrs$MYEDUC, x = dc5yrs$YNGCH, cutpoint = 10)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(dc5yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara5 <- rdd_reg_np(rdd_object=dc5yrs_reg, bw=bw_ik))

#adjust subset based on optimal bandwidth
dc5yrs_educ <- subset(dc5yrs, dc5yrs$YNGCH >= 4 & dc5yrs$YNGCH <= 16)
  
#plot regression discontinuity graph
dc_educ_plot5 <- rdplot(dc5yrs_educ$MYEDUC, x = dc5yrs_educ$YNGCH, c = 10, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "2014", x.label = "Age of Youngest Child", y.label = "Years in School")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara5, from=2, to=18, by=1, plot = FALSE)
dc_educ_bw5 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 6.691201, y = 0.8835) +
  ggtitle("2014") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r DC 4 years educ}
#dc rdd 4 years after implementation, educational attainment

#create initial subset
dc4yrs <- subset(dcmoms, dcmoms$YEAR == 2013)

#create data table for regression
dc4yrs_reg <- rdd_data(y = dc4yrs$MYEDUC, x = dc4yrs$YNGCH, cutpoint = 9)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(dc4yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara4 <- rdd_reg_np(rdd_object=dc4yrs_reg, bw=bw_ik))

#adjust subset based on optimal bandwidth
dc4yrs_educ <- subset(dc4yrs, dc4yrs$YNGCH >= 2 & dc4yrs$YNGCH <= 16)
  
#plot regression discontinuity graph
dc_educ_plot4 <-rdplot(dc4yrs_educ$MYEDUC, x = dc4yrs_educ$YNGCH, c = 9, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "2013", x.label = "Age of Youngest Child", y.label = "Years in School")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara4, from=2, to=18, by=1)
dc_educ_bw4 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 7.749977, y = -1.43739) +
  ggtitle("2013") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```


```{r DC 3 years educ}
#dc rdd 3 years after implementation, educational attainment

#create initial subset
dc3yrs_educ <- subset(dcmoms, dcmoms$YEAR == 2012)

#create data table for regression
dc3yrs_reg <- rdd_data(y = dc3yrs_educ$MYEDUC, x = dc3yrs_educ$YNGCH, cutpoint = 8, covar = dc3yrs_educ$AGE)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(dc3yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara3 <- rdd_reg_np(rdd_object=dc3yrs_reg, bw=bw_ik))

#don't need to adjust subset because bandwidth covers the entire sample
  
#plot regression discontinuity graph
dc_educ_plot3 <- rdplot(dc3yrs_educ$MYEDUC, x = dc3yrs_educ$YNGCH, c = 8, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "2012", x.label = "Age of Youngest Child", y.label = "Years in School")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara3, from=2, to=18, by=1)
dc_educ_bw3 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x =  10.01765, y = 0.75440) +
  ggtitle("2012") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r DC 2 years educ}
#DC 2 years after implementation, educational attainment

#create initial subset
dc2yrs_educ <- subset(dcmoms, dcmoms$YEAR == 2011)

#create data table for regression
dc2yrs_reg <- rdd_data(y = dc2yrs_educ$MYEDUC, x = dc2yrs_educ$YNGCH, cutpoint = 7)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(dc2yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara2 <- rdd_reg_np(rdd_object=dc2yrs_reg, bw=bw_ik))

#adjust subset based on optimal bandwidth
dc2yrs_educ <- subset(dc2yrs_educ, dc2yrs_educ$YNGCH >= 1 & dc2yrs_educ$YNGCH <= 13)

  
#plot regression discontinuity graph
dc_educ_plot2 <-rdplot(dc2yrs_educ$MYEDUC, x = dc2yrs_educ$YNGCH, c = 7, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "2011", x.label = "Age of Youngest Child", y.label = "Years in School")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara2, from=2, to=18, by=1)
dc_educ_bw2 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 6.665755, y = -1.43141) +
  ggtitle("2011") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```


```{r grid plots educ}
#make grid plots

educ_dc_grid <- grid.arrange(grobs = list(dc_educ_plot2$rdplot, dc_educ_plot3$rdplot, dc_educ_plot4$rdplot, dc_educ_plot5$rdplot), ncol = 2, nrow = 2, top = "Educational Attainment of Mothers in Washington, DC")

educ_dc_bw_grid <- grid.arrange(grobs = list(dc_educ_bw2, dc_educ_bw3, dc_educ_bw4, dc_educ_bw5), ncol = 2, nrow = 2, top = "Bandwidth Sensitivity Tests - Educational Attainment of Mothers in Washington, DC")

```


### Bachelor's Degree

```{r DC 2 years bachelor's}
#DC 2 years after implementation, bachelor's degree

#create initial subset
dc2yrs <- subset(dcmoms, dcmoms$YEAR == 2011)

#create data table for regression
dc2yrs_reg <- rdd_data(y = dc2yrs$bachelor, x = dc2yrs$YNGCH, cutpoint = 7)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(dc2yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara2 <- rdd_reg_np(rdd_object=dc2yrs_reg, bw=bw_ik))

#no subset adjustment needed because optimal bandwidth covers all observations
dc2yrs <- subset(dc2yrs, dc2yrs$YNGCH >= 0 & dc2yrs$YNGCH <= 14)
  
#plot regression discontinuity graph
dc_bachelor_plot2 <- rdplot(y = dc2yrs$bachelor*100, x = dc2yrs$YNGCH, c = 7, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "2011", x.label = "Age of Youngest Child", y.label = "% Bachelor")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara2, from=2, to=18, by=1)
dc_bachelor_bw2 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 7.335013, y = -0.15399) +
  ggtitle("2011") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r DC 3 years bachelors}
#DC 3 years after implementation, bachelor's degree

#create initial subset
dc3yrs <- subset(dcmoms, dcmoms$YEAR == 2012)

#create data table for regression
dc3yrs_reg <- rdd_data(y = dc3yrs$bachelor, x = dc3yrs$YNGCH, cutpoint = 8, covar = dc3yrs$AGE)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(dc3yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara3 <- rdd_reg_np(rdd_object=dc3yrs_reg, bw=bw_ik))

#no subset adjustment needed because optimal bandwidth covers all observations
  
#plot regression discontinuity graph
dc_bachelor_plot3 <- rdplot(y = dc3yrs$bachelor*100, x = dc3yrs$YNGCH, c = 8, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "2012", x.label = "Age of Youngest Child", y.label = "% Bachelor")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara3, from=2, to=18, by=1)
dc_bachelor_bw3 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 10.1113, y = 0.052683) +
  ggtitle("2012") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r DC 4 years bachelors}
#DC 4 years after implementation, bachelor's degree

#create initial subset
dc4yrs <- subset(dcmoms, dcmoms$YEAR == 2013)

#create data table for regression
dc4yrs_reg <- rdd_data(y = dc4yrs$bachelor, x = dc4yrs$YNGCH, cutpoint = 9, covar = dc4yrs$AGE)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(dc4yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara4 <- rdd_reg_np(rdd_object=dc4yrs_reg, bw=bw_ik))

#no subset adjustment needed because optimal bandwidth covers all observations
  
#plot regression discontinuity graph
dc_bachelor_plot4 <- rdplot(y = dc4yrs$bachelor*100, x = dc4yrs$YNGCH, c = 9, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "2013", x.label = "Age of Youngest Child", y.label = "% Bachelor")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara4, from=2, to=18, by=1)
dc_bachelor_bw4 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 9.118557, y = -0.042280) +
  ggtitle("2013") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r DC 5 years bachelors}
#DC 5 years after implementation, bachelor's degree

#create initial subset
dc5yrs <- subset(dcmoms, dcmoms$YEAR == 2014)

#create data table for regression
dc5yrs_reg <- rdd_data(y = dc5yrs$bachelor, x = dc5yrs$YNGCH, cutpoint = 10)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(dc5yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara5 <- rdd_reg_np(rdd_object=dc5yrs_reg, bw=bw_ik))

#no subset adjustment needed because optimal bandwidth covers all observations
dc5yrs <- subset(dc5yrs, dc5yrs$YNGCH >= 2 & dc5yrs$YNGCH <= 16)
  
#plot regression discontinuity graph
dc_bachelor_plot5 <- rdplot(y = dc5yrs$bachelor*100, x = dc5yrs$YNGCH, c = 10, p = 1, col.dots = "black", col.lines = "black", title = "2014", x.label = "Age of Youngest Child", y.label = "% Bachelor")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara5, from=2, to=18, by=1)
dc_bachelor_bw5 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 8.178698, y = 0.16356) +
  ggtitle("2014") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r grid plots bachelor}
#make grid plots

bachelor_dc_grid <- grid.arrange(grobs = list(dc_bachelor_plot2$rdplot, dc_bachelor_plot3$rdplot, dc_bachelor_plot4$rdplot, dc_bachelor_plot5$rdplot), ncol = 2, nrow = 2, top = "Rate of Bachelor's Degrees for Mothers in Washington, DC")

bachelor_dc_bw_grid <- grid.arrange(grobs = list(dc_bachelor_bw2, dc_bachelor_bw3, dc_bachelor_bw4, dc_bachelor_bw5), ncol = 2, nrow = 2, top = "Bandwidth Sensitivity Tests - Rates of Bachelor's Degrees for Mothers in Washington, DC")
```


### Any College Degree

```{r DC 2 years any degree}
#DC 2 years after implementation, any degree

#create initial subset
dc2yrs <- subset(dcmoms, dcmoms$YEAR == 2011)

#create data table for regression
dc2yrs_reg <- rdd_data(y = dc2yrs$associates_or_up, x = dc2yrs$YNGCH, cutpoint = 7)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(dc2yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara2 <- rdd_reg_np(rdd_object=dc2yrs_reg, bw=bw_ik))

#no subset adjustment needed because optimal bandwidth covers all observations
dc2yrs <- subset(dc2yrs, dc2yrs$YNGCH <= 16)
  
#plot regression discontinuity graph
dc_all_plot2 <- rdplot(y = dc2yrs$associates_or_up*100, x = dc2yrs$YNGCH, c = 7, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "2011", x.label = "Age of Youngest Child", y.label = "% Any College Degree")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara2, from=2, to=18, by=1)
dc_all_bw2 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 7.423477, y = -0.095095) +
  ggtitle("2011") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r DC 3 years any degree}
#DC 3 years after implementation, any degree

#create initial subset
dc3yrs <- subset(dcmoms, dcmoms$YEAR == 2012)

#create data table for regression
dc3yrs_reg <- rdd_data(y = dc3yrs$associates_or_up, x = dc3yrs$YNGCH, cutpoint = 8)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(dc3yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara3 <- rdd_reg_np(rdd_object=dc3yrs_reg, bw=bw_ik))

#adjust subset based on optimal bandwidth
dc3yrs <- subset(dc3yrs, dc3yrs$YNGCH <= 16)
  
#plot regression discontinuity graph
dc_all_plot3 <- rdplot(y = dc3yrs$associates_or_up*100, x = dc3yrs$YNGCH, c = 8, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "2012", x.label = "Age of Youngest Child", y.label = "% Any College Degree")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara3, from=2, to=18, by=1)
dc_all_bw3 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 15.598, y = 0.101174) +
  ggtitle("2012") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r DC 4 years any degree}
#DC 4 years after implementation, any degree

#create initial subset
dc4yrs <- subset(dcmoms, dcmoms$YEAR == 2013)

#create data table for regression
dc4yrs_reg <- rdd_data(y = dc4yrs$associates_or_up, x = dc4yrs$YNGCH, cutpoint = 9)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(dc4yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara4 <- rdd_reg_np(rdd_object=dc4yrs_reg, bw=bw_ik))

#no subset adjustment needed because optimal bandwidth covers all observations
  
#plot regression discontinuity graph
dc_all_plot4 <- rdplot(y = dc4yrs$associates_or_up*100, x = dc4yrs$YNGCH, c = 9, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "2013", x.label = "Age of Youngest Child", y.label = "% Any College Degree")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara4, from=2, to=18, by=1)
dc_all_bw4 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 8.682466, y = -0.12705) +
  ggtitle("2013") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r DC 5 years any degree}
#DC 5 years after implementation, any degree

#create initial subset
dc5yrs <- subset(dcmoms, dcmoms$YEAR == 2014)

#create data table for regression
dc5yrs_reg <- rdd_data(y = dc5yrs$associates_or_up, x = dc5yrs$YNGCH, cutpoint = 10)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(dc5yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara5 <- rdd_reg_np(rdd_object=dc5yrs_reg, bw=bw_ik))

#no subset adjustment needed because optimal bandwidth covers all observations
dc5yrs <- subset(dc5yrs, dc5yrs$YNGCH >= 3 & dc5yrs$YNGCH <= 15)

#plot regression discontinuity graph
dc_all_plot5 <- rdplot(y = dc5yrs$associates_or_up*100, x = dc5yrs$YNGCH, c = 10, p = 1, col.dots = "black", col.lines = "black", title = "2014", x.label = "Age of Youngest Child", y.label = "% Any College Degree")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara5, from=2, to=18, by=1)
dc_all_bw5 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 7.338641, y = 0.20016) +
  ggtitle("2014") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```
```{r grid plots all}
#make grid plots

all_dc_grid <- grid.arrange(grobs = list(dc_all_plot2$rdplot, dc_all_plot3$rdplot, dc_all_plot4$rdplot, dc_all_plot5$rdplot), ncol = 2, nrow = 2, top = "Rate of College Degrees for Mothers in Washington, DC")

all_dc_bw_grid <- grid.arrange(grobs = list(dc_all_bw2, dc_all_bw3, dc_all_bw4, dc_all_bw5), ncol = 2, nrow = 2, top = "Bandwidth Sensitivity Tests - Rates of College Degrees for Mothers in Washington, DC")
```


### Postgrad Degree

```{r DC 2 years postgrad}
#DC 2 years after implementation, postgrad

#create initial subset
dc2yrs <- subset(dcmoms, dcmoms$YEAR == 2011)

#create data table for regression
dc2yrs_reg <- rdd_data(y = dc2yrs$postgrad, x = dc2yrs$YNGCH, cutpoint = 7, covar = dc2yrs$AGE)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(dc2yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara2 <- rdd_reg_np(rdd_object=dc2yrs_reg, bw=bw_ik))

#no subset adjustment needed because optimal bandwidth covers all observations
dc2yrs <- subset(dc2yrs, dc2yrs$YNGCH <= 16)

#plot regression discontinuity graph
dc_postgrad_plot2 <- rdplot(y = dc2yrs$postgrad*100, x = dc2yrs$YNGCH, c = 7, p = 1, col.dots = "black", col.lines = "black", title = "2011", x.label = "Age of Youngest Child", y.label = "% Postgraduate Degree")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara2, from=2, to=18, by=1)
dc_postgrad_bw2 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 6.744515, y = -0.17447) +
  ggtitle("2011") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r DC 3 years postgrad}
#DC 3 years after implementation, postgrad

#create initial subset
dc3yrs <- subset(dcmoms, dcmoms$YEAR == 2012)

#create data table for regression
dc3yrs_reg <- rdd_data(y = dc3yrs$postgrad, x = dc3yrs$YNGCH, cutpoint = 8)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(dc3yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara3 <- rdd_reg_np(rdd_object=dc3yrs_reg, bw=bw_ik))

#no subset adjustment needed because optimal bandwidth covers all observations

#plot regression discontinuity graph
dc_postgrad_plot3 <- rdplot(y = dc3yrs$postgrad*100, x = dc3yrs$YNGCH, c = 8, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "2012", x.label = "Age of Youngest Child", y.label = "% Postgraduate Degree")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara3, from=2, to=18, by=1)
dc_postgrad_bw3 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 9.572123, y = -0.015219) +
  ggtitle("2012") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r DC 4 years postgrad}
#DC 4 years after implementation, postgrad

#create initial subset
dc4yrs <- subset(dcmoms, dcmoms$YEAR == 2013)

#create data table for regression
dc4yrs_reg <- rdd_data(y = dc4yrs$postgrad, x = dc4yrs$YNGCH, cutpoint = 9)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(dc4yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara4 <- rdd_reg_np(rdd_object=dc4yrs_reg, bw=bw_ik))

#no subset adjustment needed because optimal bandwidth covers all observations

#plot regression discontinuity graph
dc_postgrad_plot4 <- rdplot(y = dc4yrs$postgrad*100, x = dc4yrs$YNGCH, c = 9, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "2013", x.label = "Age of Youngest Child", y.label = "% Postgraduate Degree")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara4, from=2, to=18, by=1)
dc_postgrad_bw4 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 6.514625, y = -0.17308) +
  ggtitle("2013") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r DC 5 years postgrad}
#DC 5 years after implementation, postgrad

#create initial subset
dc5yrs <- subset(dcmoms, dcmoms$YEAR == 2014)

#create data table for regression
dc5yrs_reg <- rdd_data(y = dc5yrs$postgrad, x = dc5yrs$YNGCH, cutpoint = 10)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(dc5yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara5 <- rdd_reg_np(rdd_object=dc5yrs_reg, bw=bw_ik))

#no subset adjustment needed because optimal bandwidth covers all observations
dc5yrs <- subset(dc5yrs, dc5yrs$YNGCH >= 2 & dc5yrs$YNGCH <= 16)

#plot regression discontinuity graph
dc_postgrad_plot5 <- rdplot(y = dc5yrs$postgrad*100, x = dc5yrs$YNGCH, c = 10, p = 1, col.dots = "black", col.lines = "black", title = "2014", x.label = "Age of Youngest Child", y.label = "% Postgraduate Degree")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara5, from=2, to=18, by=1)
dc_postgrad_bw5 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 7.874217, y = 0.097313) +
  ggtitle("2014") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r grid plots postgrad}
#make grid plots

postgrad_dc_grid <- grid.arrange(grobs = list(dc_postgrad_plot2$rdplot, dc_postgrad_plot3$rdplot, dc_postgrad_plot4$rdplot, dc_postgrad_plot5$rdplot), ncol = 2, nrow = 2, top = "Rate of Postgraduate Degrees for Mothers in Washington, DC")

postgrad_dc_bw_grid <- grid.arrange(grobs = list(dc_postgrad_bw2, dc_postgrad_bw3, dc_postgrad_bw4, dc_postgrad_bw5), ncol = 2, nrow = 2, top = "Bandwidth Sensitivity Tests - Rates of Postgraduate Degrees for Mothers in Washington, DC")
```
## RDD Assumption Checks

### Discontinuity Assumption
This checks whether important demographic variables are continuous at the cutoff point to ensure that any discontinuity found is only due to the change in treatment.

```{r discontinuity check - percent white}
#create data table for regression
race_test <- rdd_data(y = dc4yrs$white, x = dc4yrs$YNGCH, cutpoint = 9)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(dc4yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara4 <- rdd_reg_np(rdd_object=race_test, bw=bw_ik))

#adjust subset based on optimal bandwidth
dc4yrs_educ <- subset(dc4yrs, dc4yrs$YNGCH >= 2 & dc4yrs$YNGCH <= 16)
  
#plot regression discontinuity graph
race_plot <-rdplot(dc4yrs_educ$white*100, x = dc4yrs_educ$YNGCH, c = 9, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "Percent White", x.label = "Age of Youngest Child", y.label = "% White")
```

```{r discontinuity check - percent black}
#create data table for regression
race_test1 <- rdd_data(y = dc4yrs$black, x = dc4yrs$YNGCH, cutpoint = 9)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(dc4yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara4 <- rdd_reg_np(rdd_object=race_test1, bw=bw_ik))

#adjust subset based on optimal bandwidth
dc4yrs_educ <- subset(dc4yrs, dc4yrs$YNGCH >= 2 & dc4yrs$YNGCH <= 16)
  
#plot regression discontinuity graph
race_plot1 <-rdplot(dc4yrs_educ$black*100, x = dc4yrs_educ$YNGCH, c = 9, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "Percent Black", x.label = "Age of Youngest Child", y.label = "% Black")
```

```{r discontinuity check - age}
#create data table for regression
age_test <- rdd_data(y = dc4yrs$AGE, x = dc4yrs$YNGCH, cutpoint = 9)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(dc4yrs_reg)

#run regression based on optimal bandwidth
#(reg_nonpara4 <- rdd_reg_np(rdd_object=age_test, bw=bw_ik))

#adjust subset based on optimal bandwidth
dc4yrs_educ <- subset(dc4yrs, dc4yrs$YNGCH >= 2 & dc4yrs$YNGCH <= 16)
  
#plot regression discontinuity graph
age_plot <-rdplot(dc4yrs_educ$AGE, x = dc4yrs_educ$YNGCH, c = 9, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "Age of Mother", x.label = "Age of Youngest Child", y.label = "Age of Mother")
```

```{r discontinuity check - income}
#create data table for regression
income_test <- rdd_data(y = dc4yrs$HHINCOME, x = dc4yrs$YNGCH, cutpoint = 9)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(dc4yrs_reg)

#run regression based on optimal bandwidth
#(reg_nonpara4 <- rdd_reg_np(rdd_object=income_test, bw=bw_ik))

#adjust subset based on optimal bandwidth
dc4yrs_educ <- subset(dc4yrs, dc4yrs$YNGCH >= 2 & dc4yrs$YNGCH <= 16)
  
#plot regression discontinuity graph
income_plot <-rdplot(dc4yrs_educ$HHINCOME/1000, x = dc4yrs_educ$YNGCH, c = 9, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "Household Income", x.label = "Age of Youngest Child", y.label = "Income (thousands)")
```

```{r discontinuity check - marital status}
#create data table for regression
married_test <- rdd_data(y = dc4yrs$married, x = dc4yrs$YNGCH, cutpoint = 9)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(dc4yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara4 <- rdd_reg_np(rdd_object=married_test, bw=bw_ik))

#adjust subset based on optimal bandwidth
dc4yrs_educ <- subset(dc4yrs, dc4yrs$YNGCH >= 2 & dc4yrs$YNGCH <= 16)
  
#plot regression discontinuity graph
married_plot <-rdplot(dc4yrs_educ$married*100, x = dc4yrs_educ$YNGCH, c = 9, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "Marital Status", x.label = "Age of Youngest Child", y.label = "% Married")
```

```{r}
continuity_dc_grid <- grid.arrange(grobs = list(race_plot$rdplot, race_plot1$rdplot, income_plot$rdplot, age_plot$rdplot, married_plot$rdplot), ncol = 3, nrow = 2, top = "Covariate Continuity Tests - Washington, DC")
```


### Bin Size
```{r}
#regular regression discontinuity graph, nbins = 3
dc_bin3 <-rdplot(dc4yrs_educ$MYEDUC, x = dc4yrs_educ$YNGCH, c = 9, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "3 Bins", x.label = "Age of Youngest Child", y.label = "Years in School", nbins = 3)

#regular regression discontinuity graph, nbins = 5
dc_bin5 <-rdplot(dc4yrs_educ$MYEDUC, x = dc4yrs_educ$YNGCH, c = 9, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "5 Bins", x.label = "Age of Youngest Child", y.label = "Years in School", nbins = 5)

#regular regression discontinuity graph, nbins = 10
dc_bin10 <-rdplot(dc4yrs_educ$MYEDUC, x = dc4yrs_educ$YNGCH, c = 9, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "10 Bins", x.label = "Age of Youngest Child", y.label = "Years in School", nbins = 10)

dc_bin50 <-rdplot(dc4yrs_educ$MYEDUC, x = dc4yrs_educ$YNGCH, c = 9, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "50 Bins", x.label = "Age of Youngest Child", y.label = "Years in School", nbins = 50)
```

```{r}
bin_fl_grid <- grid.arrange(grobs = list(dc_bin3$rdplot, dc_bin5$rdplot, dc_bin10$rdplot, dc_bin50$rdplot), ncol = 2, nrow = 2, top = "Bin Size Test - Washington, DC")
```

### Polynomials
```{r}
#regular regression discontinuity graph, p = 1
dc_poly1 <-rdplot(dc4yrs_educ$MYEDUC, x = dc4yrs_educ$YNGCH, c = 9, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "Linear (Polynomial = 1)", x.label = "Age of Youngest Child", y.label = "Years in School")

#regular regression discontinuity graph, p = 2
dc_poly2 <-rdplot(dc4yrs_educ$MYEDUC, x = dc4yrs_educ$YNGCH, c = 9, p = 2, masspoints = "off", col.dots = "black", col.lines = "black", title = "Polynomial = 2", x.label = "Age of Youngest Child", y.label = "Years in School")

#regular regression discontinuity graph, p = 3
dc_poly3 <-rdplot(dc4yrs_educ$MYEDUC, x = dc4yrs_educ$YNGCH, c = 9, p = 3, masspoints = "off", col.dots = "black", col.lines = "black", title = "Polynomial = 3", x.label = "Age of Youngest Child", y.label = "Years in School")

```

```{r}
poly_dc_grid <- grid.arrange(grobs = list(dc_poly1$rdplot, dc_poly2$rdplot, dc_poly3$rdplot), ncol = 2, nrow = 2, top = "Polynomial Test - Washington, DC")
```


