---
title: "Florida"
output: html_notebook
---

***NOTE! Run the "Data Cleaning" file before this.***

```{r Libraries, eval=FALSE, warning=FALSE, include=FALSE}
#load libraries
library(ipumsr)
library(dplyr)
library(rdrobust)
library(ggplot2)
library(rddtools)
```

Below, I run a regression discontinuity analysis using Florida data. I create a model for 2, 3, 4, and 5 years after Florida's preschool program was implemented. My running variable is the age of a woman's youngest child. First, I use educational attainment and the rate of mothers with college degrees as my outcome variables.

### Educational Attainment

```{r Florida 5 years educ}
#Florida five years after implementation, educational attainment

#create initial subset
fl5yrs_educ <- subset(floridamoms, floridamoms$YEAR == 2010)

#create data table for regression
fl5yrs_reg <- rdd_data(y = fl5yrs_educ$MYEDUC, x = fl5yrs_educ$YNGCH, cutpoint = 10)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(fl5yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara5 <- rdd_reg_np(rdd_object=fl5yrs_reg, bw=bw_ik))

#adjust subset based on optimal bandwidth
fl5yrs_educ <- subset(fl5yrs_educ, fl5yrs_educ$YNGCH >= 5 & fl5yrs_educ$YNGCH <= 15)
  
#plot regression discontinuity graph
fl_educ_plot5 <- rdplot(fl5yrs_educ$MYEDUC, x = fl5yrs_educ$YNGCH, c = 10, p = 1, col.dots = "black", col.lines = "black", title = "2010", x.label = "Age of Youngest Child", y.label = "Years in School")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara5, from=2, to=18, by=1, plot = FALSE)
fl_educ_bw5 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 5.368483, y = -0.28282) +
  ggtitle("2010") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r Florida 4 years educ}
#Florida 4 years after implementation, educational attainment

#create initial subset
fl4yrs_educ <- subset(floridamoms, floridamoms$YEAR == 2009)

#create data table for regression
fl4yrs_reg <- rdd_data(y = fl4yrs_educ$MYEDUC, x = fl4yrs_educ$YNGCH, cutpoint = 9)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(fl4yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara4 <- rdd_reg_np(rdd_object=fl4yrs_reg, bw=bw_ik))

#adjust subset based on optimal bandwidth
fl4yrs_educ <- subset(fl4yrs_educ, fl4yrs_educ$YNGCH >= 2 & fl4yrs_educ$YNGCH <= 16)
  
#plot regression discontinuity graph
fl_educ_plot4 <- rdplot(fl4yrs_educ$MYEDUC, x = fl4yrs_educ$YNGCH, c = 9, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "2009", x.label = "Age of Youngest Child", y.label = "Years in school")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara4, from=2, to=18, by=1, plot = FALSE)
fl_educ_bw4 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 7.819367, y = 0.076268) +
  ggtitle("2009") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r Florida 3 years educ}
#Florida 3 years after implementation, educational attainment

#create initial subset
fl3yrs_educ <- subset(floridamoms, floridamoms$YEAR == 2008)

#create data table for regression
fl3yrs_reg <- rdd_data(y = fl3yrs_educ$MYEDUC, x = fl3yrs_educ$YNGCH, cutpoint = 8)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(fl3yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara3 <- rdd_reg_np(rdd_object=fl3yrs_reg, bw=bw_ik))

#adjust subset based on optimal bandwidth
fl3yrs_educ <- subset(fl3yrs_educ, fl3yrs_educ$YNGCH <= 17)
  
#plot regression discontinuity graph
fl_educ_plot3 <- rdplot(fl3yrs_educ$MYEDUC, x = fl3yrs_educ$YNGCH, c = 8, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "2008", x.label = "Age of Youngest Child", y.label = "Years in school")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara3, from=2, to=18, by=1, plot = FALSE)
fl_educ_bw3 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 9.016539, y = -0.069352) +
  ggtitle("2008") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r Florida 2 years educ}
#Florida 2 years after implementation, educational attainment

#create initial subset
fl2yrs_educ <- subset(floridamoms, floridamoms$YEAR == 2007)

#create data table for regression
fl2yrs_reg <- rdd_data(y = fl2yrs_educ$MYEDUC, x = fl2yrs_educ$YNGCH, cutpoint = 7)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(fl2yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara2 <- rdd_reg_np(rdd_object=fl2yrs_reg, bw=bw_ik))

#adjust subset based on optimal bandwidth
fl2yrs_educ <- subset(fl2yrs_educ, fl2yrs_educ$YNGCH <= 16)
  
#plot regression discontinuity graph
fl_educ_plot2 <- rdplot(fl2yrs_educ$MYEDUC, x = fl2yrs_educ$YNGCH, c = 7, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "2007", x.label = "Age of Youngest Child", y.label = "Years in school")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara2, from=2, to=18, by=1, plot = FALSE)
fl_educ_bw2 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 9.443095, y = 0.0044192) +
  ggtitle("2007") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r grid plots educ}
#make grid plots

educ_fl_grid <- grid.arrange(grobs = list(fl_educ_plot2$rdplot, fl_educ_plot3$rdplot, fl_educ_plot4$rdplot, fl_educ_plot5$rdplot), ncol = 2, nrow = 2, top = "Educational Attainment of Mothers in Florida")

educ_fl_bw_grid <- grid.arrange(grobs = list(fl_educ_bw2, fl_educ_bw3, fl_educ_bw4, fl_educ_bw5), ncol = 2, nrow = 2, top = "Bandwidth Sensitivity Tests - Educational Attainment of Mothers in Florida")

```
## Bachelor's Degree

```{r Florida 2 years bachelors}
#Florida 2 years after implementation, bachelors

#create initial subset
fl2yrs_bachelor <- subset(floridamoms, floridamoms$YEAR == 2007)

#create data table for regression
fl2yrs_reg <- rdd_data(y = fl2yrs_bachelor$bachelor, x = fl2yrs_bachelor$YNGCH, cutpoint = 7)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(fl2yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara2 <- rdd_reg_np(rdd_object=fl2yrs_reg, bw=bw_ik))

#adjust subset based on optimal bandwidth
fl2yrs_bachelor <- subset(fl2yrs_bachelor, fl2yrs_bachelor$YNGCH >= 1 & fl2yrs_bachelor$YNGCH <= 13)

print(nrow(fl2yrs_bachelor))
  
#plot regression discontinuity graph
fl_bachelor_plot2 <- rdplot(y = fl2yrs_bachelor$bachelor, x = fl2yrs_bachelor$YNGCH, c = 7, p = 1, col.dots = "black", col.lines = "black", title = "2007", x.label = "Age of Youngest Child", y.label = "% Bachelor's Degree")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara2, from=2, to=18, by=1, plot = FALSE)
fl_bachelor_bw2 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 6.161375, y = -0.041500) +
  ggtitle("2007") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r Florida 3 years bachelor}
#Florida 3 years after implementation, bachelors

#create initial subset
fl3yrs_bachelor <- subset(floridamoms, floridamoms$YEAR == 2008)

#create data table for regression
fl3yrs_reg <- rdd_data(y = fl3yrs_bachelor$bachelor, x = fl3yrs_bachelor$YNGCH, cutpoint = 8)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(fl3yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara3 <- rdd_reg_np(rdd_object=fl3yrs_reg, bw=bw_ik))

#adjust subset based on optimal bandwidth
fl3yrs_bachelor <- subset(fl3yrs_bachelor, fl3yrs_bachelor$YNGCH >= 2 & fl3yrs_bachelor$YNGCH <= 14)

print(nrow(fl3yrs_bachelor))

#plot regression discontinuity graph
fl_bachelor_plot3 <- rdplot(y = fl3yrs_bachelor$bachelor, x = fl3yrs_bachelor$YNGCH, c = 8, p = 1, col.dots = "black", col.lines = "black", title = "2008", x.label = "Age of Youngest Child", y.label = "% Bachelor's degree")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara3, from=2, to=18, by=1, plot = FALSE)
fl_bachelor_bw3 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 6.685717, y = -0.008102) +
  ggtitle("2008") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r Florida 4 years bachelors}
#Florida 4 years after implementation, bachelors

#create initial subset
fl4yrs_bachelor <- subset(floridamoms, floridamoms$YEAR == 2009)

#create data table for regression
fl4yrs_reg <- rdd_data(y = fl4yrs_bachelor$bachelor, x = fl4yrs_bachelor$YNGCH, cutpoint = 9)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(fl4yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara4 <- rdd_reg_np(rdd_object=fl4yrs_reg, bw=bw_ik))

#adjust subset based on optimal bandwidth
fl4yrs_bachelor <- subset(fl4yrs_bachelor, fl4yrs_bachelor$YNGCH >= 2 & fl4yrs_bachelor$YNGCH <= 16)
print(nrow(fl4yrs_bachelor))

#plot regression discontinuity graph
fl_bachelor_plot4 <- rdplot(y = fl4yrs_bachelor$bachelor, x = fl4yrs_bachelor$YNGCH, c = 9, p = 1, col.dots = "black", col.lines = "black", title = "2009", x.label = "Age of Youngest Child", y.label = "% Bachelor's Degree")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara4, from=2, to=18, by=1, plot = FALSE)
fl_bachelor_bw4 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 7.742408, y = 0.019400) +
  ggtitle("2009") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r Florida 5 years bachelors}
#Florida five years after implementation, bachelors

#create initial subset
fl5yrs_bachelor <- subset(floridamoms, floridamoms$YEAR == 2010)

#create data table for regression
fl5yrs_reg <- rdd_data(y = fl5yrs_bachelor$bachelor, x = fl5yrs_bachelor$YNGCH, cutpoint = 10)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(fl5yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara5 <- rdd_reg_np(rdd_object=fl5yrs_reg, bw=bw_ik))

#adjust subset based on optimal bandwidth
fl5yrs_bachelor <- subset(fl5yrs_bachelor, fl5yrs_bachelor$YNGCH >= 5 & fl5yrs_bachelor$YNGCH <= 15)

print(nrow(fl5yrs_bachelor))
  
#plot regression discontinuity graph
fl_bachelor_plot5 <- rdplot(fl5yrs_bachelor$bachelor, x = fl5yrs_bachelor$YNGCH, c = 10, p = 1, col.dots = "black", col.lines = "black", title = "2010", x.label = "Age of Youngest Child", y.label = "% Bachelor's Degree")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara5, from=2, to=18, by=1, plot = FALSE)
fl_bachelor_bw5 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x =  5.823497, y = -0.030540) +
  ggtitle("2010") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r grid plots bachelor}
#make grid plots

bachelor_fl_grid <- grid.arrange(grobs = list(fl_bachelor_plot2$rdplot, fl_bachelor_plot3$rdplot, fl_bachelor_plot4$rdplot, fl_bachelor_plot5$rdplot), ncol = 2, nrow = 2, top = "Rate of Bachelor's Degrees for Mothers in Florida")

bachelor_fl_bw_grid <- grid.arrange(grobs = list(fl_bachelor_bw2, fl_bachelor_bw3, fl_bachelor_bw4, fl_bachelor_bw5), ncol = 2, nrow = 2, top = "Bandwidth Sensitivity Tests - Rate of Bachelor's Degrees for Mothers in Florida")

```

### All Degrees

```{r Florida 2 years any degree}
#Florida 2 years after implementation, any degree

#create initial subset
fl2yrs_all <- subset(floridamoms, floridamoms$YEAR == 2007)

#create data table for regression
fl2yrs_reg <- rdd_data(y = fl2yrs_all$associates_or_up, x = fl2yrs_all$YNGCH, cutpoint = 7)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(fl2yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara2 <- rdd_reg_np(rdd_object=fl2yrs_reg, bw=bw_ik))

#adjust subset based on optimal bandwidth
fl2yrs_all <- subset(fl2yrs_all, fl2yrs_all$YNGCH <= 14)
  
#plot regression discontinuity graph
fl_all_plot2 <- rdplot(y = fl2yrs_all$associates_or_up, x = fl2yrs_all$YNGCH, c = 7, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "2007", x.label = "Age of Youngest Child", y.label = "% Any College Degree")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara2, from=2, to=18, by=1, plot = FALSE)
fl_all_bw2 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 7.954536 , y = -0.01822) +
  ggtitle("2007") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r Florida 3 years any degree}
#Florida 3 years after implementation, any degree

#create initial subset
fl3yrs_all <- subset(floridamoms, floridamoms$YEAR == 2008)

#create data table for regression
fl3yrs_reg <- rdd_data(y = fl3yrs_all$associates_or_up, x = fl3yrs_all$YNGCH, cutpoint = 8)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(fl3yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara3 <- rdd_reg_np(rdd_object=fl3yrs_reg, bw=bw_ik))

#adjust subset based on optimal bandwidth
fl3yrs_all <- subset(fl3yrs_all, fl3yrs_all$YNGCH <= 16)

#plot regression discontinuity graph
fl_all_plot3 <- rdplot(y = fl3yrs_all$associates_or_up, x = fl3yrs_all$YNGCH, c = 8, p = 1, masspoints = "off", col.dots = "black", col.lines = "black", title = "2008", x.label = "Age of Youngest Child", y.label = "% Any College Degree")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara3, from=2, to=18, by=1, plot = FALSE)
fl_all_bw3 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 8.717611, y = -0.008538) +
  ggtitle("2008") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r Florida 4 years any degree}
#Florida 4 years after implementation, any degree

#create initial subset
fl4yrs_all <- subset(floridamoms, floridamoms$YEAR == 2009)

#create data table for regression
fl4yrs_reg <- rdd_data(y = fl4yrs_all$associates_or_up, x = fl4yrs_all$YNGCH, cutpoint = 9)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(fl4yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara4 <- rdd_reg_np(rdd_object=fl4yrs_reg, bw=bw_ik))

#adjust subset based on optimal bandwidth


#plot regression discontinuity graph
fl_all_plot4 <- rdplot(y = fl4yrs_all$associates_or_up, x = fl4yrs_all$YNGCH, c = 9, p = 1, col.dots = "black", col.lines = "black", title = "2009", x.label = "Age of Youngest Child", y.label = "% Any College Degree")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara4, from=2, to=18, by=1, plot = FALSE)
fl_all_bw4 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 11.96996, y = 0.00029974) +
  ggtitle("2009") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)

```

```{r Florida 5 years any degree}
#Florida five years after implementation, any degree

#create initial subset
fl5yrs_all <- subset(floridamoms, floridamoms$YEAR == 2010)

#create data table for regression
fl5yrs_reg <- rdd_data(y = fl5yrs_all$associates_or_up, x = fl5yrs_all$YNGCH, cutpoint = 10)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(fl5yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara5 <- rdd_reg_np(rdd_object=fl5yrs_reg, bw=bw_ik))

#adjust subset based on optimal bandwidth
fl5yrs_all <- subset(fl5yrs_all, fl5yrs_all$YNGCH >= 5 & fl5yrs_all$YNGCH <= 15)
  
#plot regression discontinuity graph
fl_all_plot5 <- rdplot(y = fl5yrs_all$associates_or_up, x = fl5yrs_all$YNGCH, c = 10, p = 1, col.dots = "black", col.lines = "black", title = "2010", x.label = "Age of Youngest Child", y.label = "% Any College Degree")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara5, from=2, to=18, by=1, plot = FALSE)
fl_all_bw5 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x =  5.522029, y = -0.040908) +
  ggtitle("2010") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r grid plots all}
#make grid plots

all_fl_grid <- grid.arrange(grobs = list(fl_all_plot2$rdplot, fl_all_plot3$rdplot, fl_all_plot4$rdplot, fl_all_plot5$rdplot), ncol = 2, nrow = 2, top = "Rate of College Degrees for Mothers in Florida")

all_fl_bw_grid <- grid.arrange(grobs = list(fl_all_bw2, fl_all_bw3, fl_all_bw4, fl_all_bw5), ncol = 2, nrow = 2, top = "Bandwidth Sensitivity Tests - Rate of College Degrees for Mothers in Florida")

```

### postgrad

```{r Florida 2 years postgrad}
#Florida 2 years after implementation, postgrad

#create initial subset
fl2yrs_post <- subset(floridamoms, floridamoms$YEAR == 2007)

#create data table for regression
fl2yrs_reg <- rdd_data(y = fl2yrs_post$postgrad, x = fl2yrs_post$YNGCH, cutpoint = 7)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(fl2yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara2 <- rdd_reg_np(rdd_object=fl2yrs_reg, bw=bw_ik))

#adjust subset based on optimal bandwidth
fl2yrs_post <- subset(fl2yrs_post, fl2yrs_post$YNGCH <= 17)

print(nrow(fl2yrs_post))
  
#plot regression discontinuity graph
fl_postgrad_plot2 <- rdplot(y = fl2yrs_post$postgrad, x = fl2yrs_post$YNGCH, c = 7, p = 1, col.dots = "black", col.lines = "black", title = "2007", x.label = "Age of Youngest Child", y.label = "% Postgraduate Degree")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara2, from=2, to=18, by=1)
fl_postgrad_bw2 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 10.91391 , y = 0.0079179) +
  ggtitle("2007") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r Florida 3 years postgrad}
#Florida 3 years after implementation, postgrad

#create initial subset
fl3yrs_post <- subset(floridamoms, floridamoms$YEAR == 2008)

#create data table for regression
fl3yrs_reg <- rdd_data(y = fl3yrs_post$postgrad, x = fl3yrs_post$YNGCH, cutpoint = 8)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(fl3yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara3 <- rdd_reg_np(rdd_object=fl3yrs_reg, bw=bw_ik))

#adjust subset based on optimal bandwidth
fl3yrs_post <- subset(fl3yrs_post, fl3yrs_post$YNGCH <= 17)
print(nrow(fl3yrs_post))

#plot regression discontinuity graph
fl_postgrad_plot3 <- rdplot(y = fl3yrs_post$postgrad, x = fl3yrs_post$YNGCH, c = 8, p = 1, col.dots = "black", col.lines = "black", title = "2008", x.label = "Age of Youngest Child", y.label = "% Postgraduate Degree")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara3, from=2, to=18, by=1, plot = FALSE)
fl_postgrad_bw3 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 9.923044, y = -0.0165699) +
  ggtitle("2008") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r Florida 4 years postgrad}
#Florida 4 years after implementation, postgrad

#create initial subset
fl4yrs_post <- subset(floridamoms, floridamoms$YEAR == 2009)

#create data table for regression
fl4yrs_reg <- rdd_data(y = fl4yrs_post$postgrad, x = fl4yrs_post$YNGCH, cutpoint = 9)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(fl4yrs_reg)

#adjust subset based on optimal bandwidth
fl4yrs_post <- subset(fl4yrs_post, fl4yrs_post$YNGCH >= 1 & fl4yrs_post$YNGCH <= 17)
print(nrow(fl4yrs_post))

#run regression based on optimal bandwidth
(reg_nonpara4 <- rdd_reg_np(rdd_object=fl4yrs_reg, bw=bw_ik))

#plot regression discontinuity graph
fl_postgrad_plot4 <- rdplot(y = fl4yrs_post$postgrad, x = fl4yrs_post$YNGCH, c = 9, p = 1, col.dots = "black", col.lines = "black", title = "2009", x.label = "Age of Youngest Child", y.label = "% Postgraduate Degree")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara4, from=2, to=18, by=1, plot = FALSE)
fl_postgrad_bw4 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x = 8.514494, y = 0.0021557) +
  ggtitle("2009") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)
```

```{r Florida 5 years postgrad}
#Florida five years after implementation, any degree

#create initial subset
fl5yrs_post <- subset(floridamoms, floridamoms$YEAR == 2010)

#create data table for regression
fl5yrs_reg <- rdd_data(y = fl5yrs_post$postgrad, x = fl5yrs_post$YNGCH, cutpoint = 10)

#find optimal bandwidth
bw_ik <- rdd_bw_ik(fl5yrs_reg)

#run regression based on optimal bandwidth
(reg_nonpara5 <- rdd_reg_np(rdd_object=fl5yrs_reg, bw=bw_ik))

#adjust subset based on optimal bandwidth
fl5yrs_post<- subset(fl5yrs_post, fl5yrs_post$YNGCH >= 3 & fl5yrs_post$YNGCH <= 15)
  
#plot regression discontinuity graph
fl_postgrad_plot5 <- rdplot(y = fl5yrs_post$postgrad, x = fl5yrs_post$YNGCH, c = 10, p = 1, col.dots = "black", col.lines = "black", title = "2010", x.label = "Age of Youngest Child", y.label = "% Postgraduate Degree")

#bandwidth sensitivity test
bw_test <- plotSensi(reg_nonpara5, from=2, to=18, by=1, plot = FALSE)
fl_postgrad_bw5 <- ggplot(bw_test, aes(x=bw, y=LATE)) + 
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high),alpha=0.2) +
  geom_point(x =  11.90277, y = -0.00028711) +
  ggtitle("2010") +
  xlab("Bandwidth") +
  ylab("Treatment effect") +
  geom_hline(yintercept = 0, alpha = 0.5)

```

```{r grid plots postgrad}
#make grid plots

postgrad_fl_grid <- grid.arrange(grobs = list(fl_postgrad_plot2$rdplot, fl_postgrad_plot3$rdplot, fl_postgrad_plot4$rdplot, fl_postgrad_plot5$rdplot), ncol = 2, nrow = 2, top = "Rate of Postgraduate Degrees for Mothers in Florida")

postgrad_fl_bw_grid <- grid.arrange(grobs = list(fl_postgrad_bw2, fl_postgrad_bw3, fl_postgrad_bw4, fl_postgrad_bw5), ncol = 2, nrow = 2, top = "Bandwidth Sensitivity Tests - Rate of Postgraduate Degrees for Mothers in Florida")

```
